---
title: "Recipes I use often"
---


```{r, include=FALSE}
library(DT)
library(purrr)
library(dplyr)
```

```{r, echo=FALSE, warning=FALSE}
recipes_data <- utils::read.csv("./data.csv")

prep_recipe <- function(recipe, link, notes){
  data.frame(
    Dish = paste0("<a href='",link,"'>",recipe,"</a>"),
    Notes = notes
  )
}

temp <- purrr::pmap_dfr(.l=list(recipes_data$Recipe, recipes_data$Website, recipes_data$Notes),.f=prep_recipe)

DT::datatable(
  temp, 
  escape = FALSE, 
  class = 'cell-border stripe', 
  rownames =  FALSE,
  options = list(
    columnDefs = list(list(className = 'dt-left', targets = "_all"))
    )
  )


```

## Reason for this website

I am terrible saving / remembering which recipe we use for dishes we like AND I 
do not have a Pinterest accout.  My spouse is tired of me asking her for the link 
to several recipes again and again.  And she is right, I should have a way of saving 
that info!

This is a quick attempt to build out a process to save my cooking recipes to a 
simple website.  I am also using it as a chance to test Github actions.  My goal is 
create a workflow that will run some R commands and update the website with each 
merge request and update.  This will let me add new recipe info via edits made to 
my github account (supporting my updating it via my phone, which is the easiest way for me 
to make updates when I am cooking.)
